Growth model analysis 3spp WB

### 2019-01-30 manuscriptAnalysis/MS_Analysis_3spp_WB.Rmd
added section to pull out data for Carys Jones

save(tempSlopesTidy,file = 'D:/projects/linkedModels/data/out/tempSlopesTidy.RData')

@@

  p <- array2df(ddD$q50$pBetaInt, label.x = "est") %>%
    rename(est=est,isYOY=d1,species=d2,season=d3,river=d4,year=d5) %>% filter(river == 1)

  p$speciesGG <- factor(p$species, levels = 1:3, labels = c("Brook Trout", "Brown Trout", "Atlantic Salmon"), ordered = T)
  p$seasonGG <- factor(p$season, levels = 1:4, labels = c("Spring","Summer","Autumn","Winter"), ordered = T)
  p$isYOYGG <- factor(p$isYOY, levels = 1:2, labels = c("Juvenile","Adult"), ordered = T)

  ggplot(p, aes(year,invlogit(est),color=factor(speciesGG))) + 
    geom_point(size = 2) + 
    labs( x = 'Year', y = 'Probability of detection') +
    scale_color_grey(start = 0.0, end = 0.85) +
    theme_publication() +
    facet_grid( seasonGG ~ isYOYGG)

@@

  ##################### 
  phi <- array2df(ddD$q50$phiBetaInt, label.x = "est") %>%
    rename(est=est,isYOY=d1,species=d2,season=d3,river=d4,year=d5) %>% filter(river == 1) 
  ggplot(phi, aes(year,invlogit(est),color=factor(species))) +geom_point() + facet_grid( season ~ isYOY)

@@

intsForTable <- pp %>% 
  filter(river == 'west brook', species %in% c('bkt','bnt')) %>%
  arrange(species,isYOY,seasonGG) %>%
  select(species,isYOY,seasonGG,intDown,int,intUp) %>%
  mutate(lo = round(intDown,3),mean = round(int,3),hi = round(intUp,3))

write.csv(intsForTable,file = 'D:/projects/linkedModels/data/out/intsForTable.csv')
```

@@

betasForTable <- q %>% 
  filter(river == 'west brook', species %in% c('bkt','bnt')) %>%
  arrange(species,betaGG,isYOY,seasonGG,betaGG) %>%
  select(species,betaGG,isYOY,seasonGG,betaGG,lo,median,hi) %>%
  mutate(lo = round(lo,3),median = round(median,3),hi = round(hi,3))

write.csv(betasForTable,file = 'D:/projects/linkedModels/data/out/betasForTable.csv')
```

@@

ggplot(rIAllMinusQ, aes(var, y = value2)) +
  geom_col(aes(fill = median)) +
  coord_flip() +
  scale_x_reverse('Variable', 
                     breaks = 1:7,
                     labels = c('Temp', 'Flow', 'Bkt', 'Bnt','Ats','Temp*Flow',  "Bkt*Bnt")) +
  scale_y_continuous('Relative proportion of variance explained',
                     breaks = c(-0.9, -0.25, -0.5, 0.0, 0.25, 0.5, 0.9),
                     labels = c('0.9', '0.25', '0.5\n\nBrook Trout\n', '0.0', '0.25', '0.5\n\nBrown Trout\n', '0.9')) +
  geom_text(data = summ1a, aes(y=xAxisLoc, x=7, label=paste(round(prop,2))),size = 5) +
  geom_hline(yintercept = 0) +
  #scale_color_grey(start = 0.15, end = 0.75) +
  theme_publication() +
 #  scale_fill_continuous() +
  scale_fill_distiller(name="Parameter\nestimate", palette = "RdBu", direction = 1) +
  theme(legend.position="right",             
        #legend.key = element_rect(colour = NA),
        legend.direction = "vertical",
        legend.key.size= unit(0.25, "in"),
        #    legend.margin = unit(0, "cm"),
        legend.title = element_text(face="plain")#element_blank()
        ) +
  facet_grid(season ~ ageGroup, labeller=labeller(season = labelsSeason2, ageGroup = labelAge))

>>>>

save(tempSlopesTidy,file = 'D:/projects/linkedModels/data/out/tempSlopesTidy.RData')
```

```{r Carys Jones analysis}
######
# for Carys Jones analysis
dJonesT <- 
  d2 %>% group_by(riverOrderedGG,seasonGG,year) %>%
    summarize(meanT = mean(meanTemperature, na.rm=T),
              sdT = sd(meanTemperature, na.rm=T)) %>%
    filter(riverOrderedGG == "West Brook", seasonGG == "Summer") %>%
    ungroup() %>%
    select(year,meanLen,sdLen)

#####
# Lengths
# run 'r mean lengths' chunk above

dJonesL <- 
  means %>%
    filter(season == 3, age == 1) %>%
    ungroup() %>%
    select(species,year,meanLen,sdLen)

######
# abundance
# run 'r adjusted counts' above

dJonesA <- 
  allFishBySpeciesYOY %>% 
    filter(riverOrderedGG == "West Brook", year >=2000, season == 3, isYOY == 2) %>%
    ungroup() %>%
    select(species,year,nAllFishBySpecies)

######
# phi
# run 'r p(detection)' below
# only has summer survival, may want annual survival

dJonesP <- phi %>%
  filter(season == 2, isYOYGG == 'Adult') %>%
  select(speciesGG,yearGG,phi) %>%
  rename(species = speciesGG, year = yearGG) %>%
  mutate(species = as.character(species))

dJonesAL <- left_join(dJonesA,dJonesL) 
dJonesALT <-  left_join(dJonesAL,dJonesT)
dJonesALTP <-  left_join(dJonesALT,dJonesP)

##
write.csv(dJonesALTP, file = 'D:/projects/linkedModels/dataForCarysJones/dJonesALTP.csv')
```

@@

  p <- array2df(ddD$q50$pBetaInt, label.x = "est") %>%
    rename(est=est,isYOY=d1,species=d2,season=d3,river=d4,year=d5) %>% filter(river == 1, year > 3)

  p$speciesGG <- factor(p$species, levels = 1:3, labels = c("Brook Trout", "Brown Trout", "Atlantic Salmon"), ordered = T)
  p$seasonGG <- factor(p$season, levels = 1:4, labels = c("Spring","Summer","Autumn","Winter"), ordered = T)
  p$isYOYGG <- factor(p$isYOY, levels = 1:2, labels = c("Juvenile","Adult"), ordered = T)
  p$yearGG <- p$year + 1996

  ggplot(p, aes(yearGG,invlogit(est),color=factor(speciesGG))) + 
    geom_point(size = 2) + 
    labs( x = 'Year', y = 'Probability of detection') +
    scale_color_grey(start = 0.0, end = 0.85) +
    theme_publication() +
    facet_grid( seasonGG ~ isYOYGG)

@@

  ##################### 
  phi <- array2df(ddD$q50$phiBetaInt, label.x = "est") %>%
    rename(est=est,isYOY=d1,species=d2,season=d3,river=d4,year=d5) %>% filter(river == 1, year > 3)

  phi$speciesGG <- factor(phi$species, levels = 1:3, labels = c("bkt", "bnt", "ats"), ordered = T)
  phi$seasonGG <- factor(phi$season, levels = 1:4, labels = c("Spring","Summer","Autumn","Winter"), ordered = T)
  phi$isYOYGG <- factor(phi$isYOY, levels = 1:2, labels = c("Juvenile","Adult"), ordered = T)
  phi$yearGG <- phi$year + 1996
  phi$phi <- invlogit(phi$est)

  ggplot(phi, aes(yearGG,phi,color=factor(speciesGG))) +geom_point() + facet_grid(seasonGG ~ isYOYGG)

@@

intsForTable <- pp %>% 
  filter(river == 'west brook', species %in% c('bkt','bnt')) %>%
  arrange(species,isYOY,seasonGG) %>%
  mutate(lo = round(intDown,3),mean = round(int,3),hi = round(intUp,3)) %>%
  select(species,isYOY,seasonGG,intDown,int,intUp)

write.csv(intsForTable,file = 'D:/projects/linkedModels/data/out/intsForTableAgeGroup.csv')
```

@@

betasForTable <- q %>% 
  filter(river == 'west brook', species %in% c('bkt','bnt')) %>%
  arrange(species,betaGG,isYOY,seasonGG,betaGG) %>%
  mutate(lo = round(lo,3),median = round(median,3),hi = round(hi,3)) %>%
  select(species,betaGG,isYOY,seasonGG,betaGG,lo,median,hi)

write.csv(betasForTable,file = 'D:/projects/linkedModels/data/out/betasForTableAgeGroup.csv')
```

@@

# bars colered by beta
ggplot(rIAllMinusQ, aes(var, y = value2)) +
  geom_col(aes(fill = median)) +
  coord_flip() +
  scale_x_reverse('Variable', 
                     breaks = 1:7,
                     labels = c('Temp', 'Flow', 'Bkt', 'Bnt','Ats','Temp*Flow',  "Bkt*Bnt")) +
  scale_y_continuous('Relative proportion of variance explained',
                     breaks = c(-0.9, -0.25, -0.5, 0.0, 0.25, 0.5, 0.9),
                     labels = c('0.9', '0.25', '0.5\n\nBrook Trout\n', '0.0', '0.25', '0.5\n\nBrown Trout\n', '0.9')) +
  geom_text(data = summ1a, aes(y=xAxisLoc, x=7, label=paste(round(prop,2))),size = 5) +
  geom_hline(yintercept = 0) +
  #scale_color_grey(start = 0.15, end = 0.75) +
  theme_publication() +
 #  scale_fill_continuous() +
  scale_fill_distiller(name="Parameter\nestimate", palette = "RdBu", direction = 1) +
  theme(legend.position="right",             
        #legend.key = element_rect(colour = NA),
        legend.direction = "vertical",
        legend.key.size= unit(0.25, "in"),
        #    legend.margin = unit(0, "cm"),
        legend.title = element_text(face="plain")#element_blank()
        ) +
  facet_grid(season ~ ageGroup, labeller=labeller(season = labelsSeason2, ageGroup = labelAge))
